\subsection{Designing software for traffic generation and control}
\label{software-drivers}

The available function calls are organized into three categories; \fullref{software-drivers-program}, \fullref{software-drivers-setup} and \fullref{software-drivers-memfunc}.

\subsubsection{Injection program example}
\label{software-drivers-program}

The default driver files include an injection program example as the \textbf{inj\_program()} function, which can be reviewed on the \autoref{appendix-programexample}. 
Using this function, the main points can be understood to be able to design an injection program with the available drivers. 
This program is used for the program setup that generates transactions of a particular type, while inserting \textbf{DELAY} between transaction batches if desired. 
First, let's understand the variables the \textbf{inj\_program()} function admits as input.

\begin{itemize}
  \item \textbf{DESC\_N\_BATCH}: The number of descriptors the injection program will contain. This variable must be at least 2 if inserting \textbf{DELAY} descriptors is desired and less than the available internal memory space implemented on the injector core. Review \fullref{} for further information.
  \item \textbf{DESC\_TYPE}: The type of traffic to be generated. At the moment, it allows the traffic generation of \textbf{READ}, \textbf{WRITE}, \textbf{READ\_FIX} or \textbf{WRITE\_FIX} transactions.
  \item \textbf{INJ\_QUEUE}: Enables the \textbf{QUEUE\_MODE\_EN} parameter during the configuration of the injector, setting the injector in an execution loop of the injection program.
  \item \textbf{SIZE\_RD\_WR}: Number of bytes that are accessed during the execution of a descriptor iteration of \textbf{READ}, \textbf{WRITE}, \textbf{READ\_FIX} or \textbf{WRITE\_FIX} type.
  \item \textbf{DESC\_ATTACK\_ADDR}: Pointer of the starting address where the traffic being generated accesses.
  \item \textbf{SIZE\_DELAY}: Number of clock cycles to be on standby between the execution of the descriptors of type \textbf{DESC\_TYPE} descriptor types. If zero, no \textbf{DELAY} descriptors will be added to the program.
\end{itemize}
\vspace{15px}

At the start of the function body, there's a number of initialization variables that use specific structs of the driver. 
These are used to set up the appropriated configuration of the injector and manage the different descriptors to upload on the injector as an injection program. 
The \autoref{table:structs} compiles the different parameters to be set on each of these structs variables.

\begin{table}[h]
  \begin{tabular}{@{}p{0.15\linewidth}x{0.2\linewidth}p{0.45\linewidth}@{}}
    \toprule
    \multicolumn{1}{c}{Struct.parameter name} & \multicolumn{1}{c}{Admissible value range} & \multicolumn{1}{c}{Description of the parameter}                                                                             \\
    \cmidrule{1-3}
    desc\_ctrl.last           & {[}0-1{]}            & Last descriptor flag on injection program.                                                                                                                         \\
    desc\_ctrl.type           & {[}0-6{]}            & Descriptor type encoding. Use the descriptor name type listed on \autoref{table:descriptors} while adding \textbf{INJ\_OP\_} as a prefix.                          \\
    desc\_ctrl.irq\_compl\_en & {[}0-1{]}            & Send an interruption through the APB network on descriptor execution completion.                                                                                   \\
    desc\_ctrl.count          & {[}0-63{]}           & Set a number of descriptor execution iterations equal to \textbf{COUNT}+1.                                                                                         \\
    desc\_ctrl.size           & {[}1-524288{]}       & Set the number of bytes to access or the number of clock cycles to wait on standby depending on the descriptor type on a single execution iteration.               \\
    desc\_delay.ctrl          & Struct               & Nested struct parameter of type \textbf{desc\_ctrl}.                                                                                                               \\
    desc\_rd\_wr.ctrl         & Struct               & Nested struct parameter of type \textbf{desc\_ctrl}.                                                                                                               \\
    desc\_rd\_wr.act\_addr    & {[}0x0-0xFFFFFFFF{]} & Variable that sets the \textbf{ATTACK\_ADDR} on descriptors that use the descriptor type \textbf{READ}, \textbf{WRITE}, \textbf{READ\_FIX} or \textbf{WRITE\_FIX}. \\
    \bottomrule
  \end{tabular}
\caption{Struct types used on the injector configuration and programming drivers.}
\label{table:structs}
\end{table}

The \textbf{inj\_config} struct has been omitted from the \autoref{table:structs} due to containing the same parameters previously explained on 
\autoref{table:configuration}.

After setting the desired structs, namely an \textbf{desc\_rd\_wr} for the traffic generation, \textbf{inj\_config} for the injector configuration and 
\textbf{desc\_delay} in case the insertion of \textbf{DELAY} descriptors is desired between transaction descriptors. 
The function proceeds by loading the descriptors in execution order to the injector and, at last, the injector configuration using setup calls which are 
explained on \fullref{software-drivers-setup}.


\subsubsection{Injection setup functions}
\label{software-drivers-setup}

The setup functions are used to parse the struct variables to actual 32-bit words following the machine format the injector understands, to then be written 
on the injector using the memory access functions presented on \autoref{software-drivers-memfunc}, or also to perform control functions like a status check.
The following list compiles all available setup functions.

\begin{itemize}
  \item \textbf{inj\_setup()}: It accepts a \textbf{inj\_config} struct variable pointer as input, which reorganizes and writes on the injector. This function is commonly used after having uploaded the injection program, since this may start the execution of the program.
  \item \textbf{inj\_reset()}: Doesn't have any input, setting the configuration to zeros, except the \textbf{RESET\_SW} parameter that is set to 1, resetting the all injector's components including the loaded injection program.
  \item \textbf{inj\_check\_run()}: Doesn't have any input. This function returns 1 if the actual injector configuration has \textbf{ENABLE} parameter asserted, meaning it is running.
  \item \textbf{setup\_descriptor\_control()}: It accepts a \textbf{desc\_ctrl} struct variable pointer as input, which reorganizes and writes on the injector as word of a descriptor. This call should never be used on an injector program directly, since it is more organized to use it on a specific descriptor type setup calls.
  \item \textbf{setup\_descriptor\_delay()}: It accepts a \textbf{desc\_delay} struct variable pointer as input, which reorganizes and writes on the injector as word of a descriptor of \textbf{DELAY} type.
  \item \textbf{setup\_descriptor\_rd\_wr()}: It accepts a \textbf{desc\_rd\_wr} struct variable pointer as input, which reorganizes and writes on the injector as words of a descriptor of \textbf{READ}, \textbf{WRITE}, \textbf{READ\_FIX} or \textbf{WRITE\_FIX} types.
\end{itemize}
\vspace{15px}


\subsubsection{Injection memory access functions}
\label{software-drivers-memfunc}

The memory access functions are functions used to execute read and writes on the APB memory space allocated for the injector.
A difference between the memory access and the setup functions is that these only work with 32-bit data words without knowledge on the actual application of the 
access.
It is recommended, for best organization, to use the following memory access functions through setup functions and not directly on an injection program.

\begin{itemize}
  \item \textbf{inj\_read\_reg()}: Returns a 32-bit word with the data read from the APB \textbf{INJ\_BASE\_ADDR} + (\textbf{entry}*4) address.
  \item \textbf{inj\_write\_reg()}: Writes the input integer \textbf{value} on the APB \textbf{INJ\_BASE\_ADDR} + (\textbf{entry}*4) address.
\end{itemize}
\vspace{15px}

For the variable input \textbf{entry} of these functions, it can be used the \textbf{INJ\_POINTER\_CONFIG} and \textbf{INJ\_POINTER\_PROGRAM} constants to 
access the APB configuration or input a descriptor word to the internal program memory of the injector, respectively.

The memory access functions have a limitation set where the access is restricted to the APB memory space used to allocate the injector, providing low-level 
protection against erroneous address access while using the injector drivers. 
This is achieved by using the variables \textbf{APB\_MEM\_SPACE} and \textbf{INJ\_BASE\_ADDR} as a limiter and pointer to the base address of the injector 
allocation on the APB memory space.
Both variables are located on the driver file \textbf{injector.h}, like all the other constants of the drivers, and they must be updated accordingly to the implementation.

